Paper 2, Econ 980x

### 2022-12-10 Paper2.Rmd
commit

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(janitor)
library(ggthemes)
library(stargazer)
#library(tinytex)
library(ipumsr)

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(janitor)
library(ggthemes)
library(stargazer)
library(tinytex)
library(ipumsr)

@@

# W emp*gender
time_model2 <- newcsv1 %>%
  mutate(year = as.character(year)) %>%
  lm(formula = bls_leis ~ gender + year + gender*year + age + race + new_educ + emp*year)

summary(time_model2)

@@

```{r tables, results = "asis"}

stargazer(time_model, time_model1, time_model2, title="Models for Change in Leisure", align=TRUE, type = "html")
